Plotting

### 2019-02-19 studysite_plot.Rmd
Updated

# Plotting with pixel boxes
fig1 <- ggplot() +#coord_equal() + 
  geom_raster(data = sa_bathy, aes(x = lon, y = lat, fill = depth)) +
  #geom_raster(data = isobath200, aes(x = lon, y = lat, fill = coast)) +
  stat_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth, alpha = ..level..), 
               colour = "black", size = 0.2, binwidth = 200, na.rm = TRUE, show_guide = FALSE) +
  geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group), 
               size = 1, colour = "black", fill = "white") +
  geom_path(data = sa_provinces_new, aes(x = long, y = lat, group = group)) +
  geom_polygon(data = wcBox, aes(x = lon, y = lat, group = group), alpha = 0.20, 
               colour = "bisque1", fill = "bisque1") +
  geom_point(data = metaData2, aes(x = lon, y = lat), alpha = 0.8, size = 1.6) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "white", shape = 0, alpha = 0.8, size = 2.1) +
  geom_rect(data = test, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), 
            alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  scale_alpha_continuous(breaks = c(-200, -1000, -2000, -3000, -4000, -5000),
                         guide_legend(title = "depth (m)")) +
  scale_fill_gradient(low = "dodgerblue4", high = "dodgerblue", na.value = "steelblue4", 
                      breaks = c(-1000, -2000, -3000, -4000, -5000),
                      guide_legend(title = "depth (m)")) +
  labs(title = NULL, x = NULL, y = NULL) +
  guides(colour = guide_legend(override.aes = list(size = 3))) +
  #guide_legend(ncol = 2) +
  theme(legend.key = element_rect(colour = NA, size = 0.2),
        legend.key.height = unit(0.4, "cm"),
        legend.background = element_blank()) +
        #legend.justification = c(1,0), legend.position = c(0.5, 0.4)) +
  coord_cartesian(xlim = sa_lons, ylim = sa_lats)
```

>>>>

# Plotting with pixel boxes
fig1 <- ggplot() +#coord_equal() + 
  geom_raster(data = sa_bathy, aes(x = lon, y = lat, fill = depth)) +
  #geom_raster(data = isobath200, aes(x = lon, y = lat, fill = coast)) +
  stat_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth, alpha = ..level..), 
               colour = "black", size = 0.2, binwidth = 200, na.rm = TRUE, show_guide = FALSE) +
  geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group), 
               size = 0.5, colour = "black", fill = "white") +
  #geom_path(data = sa_provinces_new, aes(x = long, y = lat, group = group)) +
  geom_polygon(data = wcBox, aes(x = lon, y = lat, group = group), alpha = 0.20, 
               colour = "bisque1", fill = "bisque1") +
  geom_point(data = metaData2, aes(x = lon, y = lat), alpha = 0.8, size = 1.6) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "white", shape = 0, alpha = 0.8, size = 2.1) +
  geom_rect(data = test, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), 
            alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  scale_alpha_continuous(breaks = c(-200, -1000, -2000, -3000, -4000, -5000),
                         guide_legend(title = "depth (m)")) +
  scale_fill_gradient(low = "dodgerblue4", high = "dodgerblue", na.value = "steelblue4", 
                      breaks = c(-1000, -2000, -3000, -4000, -5000),
                      guide_legend(title = "depth (m)")) +
  labs(title = NULL, x = NULL, y = NULL) +
  guides(colour = guide_legend(override.aes = list(size = 3))) +
  #guide_legend(ncol = 2) +
  theme(legend.key = element_rect(colour = NA, size = 0.2),
        legend.key.height = unit(0.4, "cm"),
        legend.background = element_blank()) +
        #legend.justification = c(1,0), legend.position = c(0.5, 0.4)) +
  coord_cartesian(xlim = sa_lons, ylim = sa_lats)
```
